Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support).

### 2017-02-09 csf-2017/paper.tex
lr

\subsection{Discussion/comparison with related Dreyer-Neis-Birkedal and with Hur-Dreyer}
\todo[inline]{Add discussion/comparison to other LRs}
% Comparisson of LR to other work:
% - Single othorgonal closure
%   o all capabilities are possible continuations, not just the one we
%   intend to be it.
% - No termination guarantees in observation relation
% - Private/public transitions used like in Dreyer-Neis-Birkedal, but
%   also to  handle the difference in what local and global
%   capabilities can handle.

>>>>

\subsection{Discussion}
%/comparison with related Dreyer-Neis-Birkedal and with Hur-Dreyer}
%\todo[inline]{Add discussion/comparison to other LRs}
% Comparisson of LR to other work:
% - Single othorgonal closure
%   o all capabilities are possible continuations, not just the one we
%   intend to be it.
% - No termination guarantees in observation relation
% - Private/public transitions used like in Dreyer-Neis-Birkedal, but
%   also to  handle the difference in what local and global
%   capabilities can handle.

\todo[inline]{Maybe move this subsection to related work}

As already mentioned, our the state transition systems used in our
logical relation are inspired by earlier work on logical relations for
high-level
languages~\cite{Ahmed:popl09, Dreyer:jfp12,Devriese:2016ObjCap}.
The idea of public and private transitions comes from 
Dreyer et. al.~\cite{Dreyer:jfp12}, who gave a logical relations model
of a high-level lambda calculus. In \emph{loc. cit.}
public transitions were used to 
capture the \emph{extensional} behavior of a program expression
(and a context), whereas private transitions were used to capture
the internal behaviour of a computation using local state.
Technically, the logical relation of Dreyer et. al.\ was
formulated using biorthogonal closure, and the future world
relation for continuations was required to be a public future world
relation. In other words, the choice between private or public future
rested on the ``structure'' of the programming language. 
In contrast, 
for our low-level, unstructured, assembly language, we
we instead decide on whether to use a private or public future 
world depending on whether the capability is global or local. 
Another interesting technical difference is that in our low-level 
language we do not have a fixed calling convention and any register
can serve as a continuation, and therefore we do not use biorthogonal
closure but just model return pointers as continuations using a single
orthogonal closure.

\lars{don't know if we need the following paragraph:}
(Even though 
Hur and Dreyer~\cite{Hur:2011:KLR:1926385.1926402} also
considered a logical
relation involving an assembly language, they still used
biorthogonal closure but that was because their logical relation
was a relation between a high-level language and an assembly
language,  and thus the assembly language in the relation essentially
inherited structure from the high-level language.)
